Stability

### 2022-10-11 Rmd/Stability.Rmd
Gross index analysed

# join tables 
full2=full_join(cv_1Fruit2, cv_1Seed2, by = c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., cv_1pollinator2, by=c('Plant_gen_sp', 'Site_ID')) %>%
  full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., S2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds,   cv_1_visitation=visitatio_rate,S_total=richness.x, S_mean=richness.y)

full2$log_VR <- unlist(full2$log_VR)
full2$syncLM <- unlist(full2$syncLM)

@@

@@

C- log VR ~ mean richness

@@

D- Loreau & Mazancourt syncrony index ~  mean richness

@@

@@

C) mean richness + log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

@@

D) mean richness + Lorea & Mazancourt index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

@@

>>>>

#Gross et al. 2014
av_sync <- function(x, w = TRUE){
 xx<-x[,which(colSums(x) > 0)]
 S <- ncol(xx) #num sp
 total <- rowSums(xx)
 p <- colSums(xx)/sum(colSums(xx)) #rel abund
 cors <- c()
 for(i in 1:ncol(xx)) cors[i] <- cor(xx[,i],total-xx[,i])
if(w){
   out <- sum(p * cors) #a--b, a-c, ...
 }else{
   out <- (1/S) * sum(cors) #a--b, a-c, ...
 }
 out
}

syn_G2=prueba%>%
 group_by(Plant_gen_sp,Site_ID)%>%
 do(av_sync=av_sync(.[4:ncol(prueba)]))

# join tables 
full2=full_join(cv_1Fruit2, cv_1Seed2, by = c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., cv_1pollinator2, by=c('Plant_gen_sp', 'Site_ID')) %>%
  full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., S2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_G2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds,   cv_1_visitation=visitatio_rate,S_total=richness.x, S_mean=richness.y)

full2$log_VR <- unlist(full2$log_VR)
full2$syncLM <- unlist(full2$syncLM)
full2$ av_sync <- unlist(full2$ av_sync)

@@

Correlacion indices sincronia
```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

# correlacion indices de sincronia

syn_cor<-full2 %>% select(log_VR,syncLM,av_sync)

## Replace Inf and -Inf with NA
syn_cor[is.na(syn_cor) | syn_cor == "Inf"] <- 0 
syn_cor[is.na(syn_cor) | syn_cor == "-Inf"] <- 0

syn_cor <- mutate_all(syn_cor, ~replace(., is.na(.), 0))

cr_syn=cor(syn_cor)

cr_syn %>% 
    kable("latex",booktabs = TRUE, digits =  4)

@@

C- Gross index ~ Total richness

rich_Gross<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(av_sync ~ S_total,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich_Gross<-rich_Gross %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich_Gross %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich_Gross$p.value < 0.05| is.na(rich_Gross$p.value), T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

#model plot
rich_Gross.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(av_sync ~ S_total,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich_Gross.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(y =  av_sync, x = S_total))+ 
  labs(y = "av_sync",x="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich_Gross.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(y =  av_sync, x = S_total))+ 
  labs(y = "av_sync",x="total richness",subtitle = "C.ladanifer")+ scale_x_continuous(limits = c(9, 27))+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich_Gross.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(y =  av_sync, x = S_total))+ 
  labs(y = "av_sync",x="total richness",subtitle = "C.salviifolius")+ scale_x_continuous(limits = c(7, 31))+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich_Gross.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(y =  av_sync, x = S_total))+ labs(y = "av_sync",x="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich_Gross.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(y =  av_sync, x = S_total))+ 
  labs(y = "av_sync",x="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

D- log VR ~ mean richness

@@

E- Loreau & Mazancourt syncrony index ~  mean richness

@@

C- Gross index ~ mean richness

#model
rich_mean_Gross<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(av_sync ~ S_mean,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich_mean_Gross<-rich_mean_Gross %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich_mean_Gross %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich_mean_Gross$p.value < 0.05| is.na(rich_mean_Gross$p.value), T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

#model plot
rich_mean_Gross.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(av_sync ~ S_mean,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich_mean_Gross.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(y =  av_sync, x = S_mean))+ 
labs(y = "av_sync",x="mean richness",subtitle = "C.crispus")+theme_classic() +theme(text = element_text(size=rel(3)))

p2=rich_mean_Gross.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(y =  av_sync, x = S_mean))+ 
  labs(y = "av_sync",x="mean richness",subtitle = "C.ladanifer") + scale_x_continuous(limits = c(4.5, 11)) + theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich_mean_Gross.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(y =  av_sync, x = S_mean))+ labs(y = "av_sync",x="mean richness",subtitle = "C.salviifolius")+ scale_x_continuous(limits = c(4, 12))+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich_mean_Gross.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(y =  av_sync, x = S_mean))+labs(y = "av_sync",x="mean richness",subtitle = "H.halimifolium")+  theme_classic() +theme(text = element_text(size=rel(3)))

p6=rich_mean_Gross.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(y =  av_sync, x = S_mean))+ labs(y = "av_sync",x="mean richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

C) total richness + Gross index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model: total richness + Gross index
sta_polli_Gross<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

sta_polli_Gross<-sta_polli_Gross %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_polli_Gross %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_polli_Gross$p.value < 0.05|is.na(sta_polli_Gross$p.value), T, F))%>%
  kable_styling(position="center", latex_option="hold_position")

#goodness of fit measures
sta_polli_Gross_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table9<-sta_polli_Gross_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

# model plot (cv_1_visitation~total richness)
sta_polli_Gross.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))

p1=sta_polli_Gross.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Gross.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "C.ladanifer") + scale_x_continuous(limits = c(9, 27))+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli_Gross.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = cv_1_visitation))+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.salviifolius") + scale_x_continuous(limits = c(7, 31))+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=sta_polli_Gross.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic() +theme(text = element_text(size=rel(3)))

p6=sta_polli_Gross.2$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

# model plot (cv_1_visitation~av_sync)
sta_polli_Gross.3 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "av_sync"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
 geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))

p1=sta_polli_Gross.3$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.crispus")+ theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Gross.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli_Gross.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.salviifolius")+ theme_classic()+theme(text = element_text(size=rel(3)))

p5=sta_polli_Gross.3$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli_Gross.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

D) mean richness + log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

@@

E) mean richness + Lorea & Mazancourt index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

@@

F) mean richness + Gross index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model: mean richness + Gross index
sta_polli_Smean_Gross<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

sta_polli_Smean_Gross<-sta_polli_Smean_Gross %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

sta_polli_Smean_Gross %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(sta_polli_Smean_Gross$p.value <0.05|is.na(sta_polli_Smean_Gross$p.value), T, F))%>%
  kable_styling(position="center", latex_option="hold_position")

#goodness of fit measures
sta_polli_Smean_Gross_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table11<-sta_polli_Smean_Gross_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

table11 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
  kable_styling(font_size = 8,full_width = F, position="left")

sta_polli_Smean_Gross2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
  mutate(mod = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=sta_polli_Smean_Gross2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Smean_Gross2$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic() +theme(text = element_text(size=rel(3)))

p3=sta_polli_Smean_Gross2$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=sta_polli_Smean_Gross2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "H.halimifolium")+theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli_Smean_Gross2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "L.pedunculata")+ theme_classic()+theme(text = element_text(size=rel(3)))

sta_polli_Smean_Gross3 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
  mutate(mod = list(ggeffects::ggpredict(mod, terms = "av_sync"))) %>%
  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
 geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=sta_polli_Smean_Gross3$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.crispus")+ theme_classic()+theme(text = element_text(size=rel(3)))

p2=sta_polli_Smean_Gross3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=sta_polli_Smean_Gross3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=sta_polli_Smean_Gross3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=sta_polli_Smean_Gross3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic() +theme(text = element_text(size=rel(3)))
